Recalibrating Gravitational Wave Phenomenological Waveform Model

### 2023-06-26 src/tex/ms.tex
minor update

In order to optimize the coefficients, we need to define a loss function that
quantifies the difference between the waveform model and the target NR simulations which we want to match.
Here we adopt a quantity commonly used in GW physics called the \textit{mismatch} function \citep{Owen:1995tm, husa2016frequency}. 
It is defined as
\begin{align} \label{eq:mismatch}
	\mathcal{M}(h_1, h_2)=1-\max_{t_0, \phi_0}\langle \hat{h}_1, \hat{h}_2\rangle,
\end{align}
where $h_{1,2}$ are the two GW waveforms we are comparing, and $t_0$ and $\phi_0$
are a relative time and phase shift respectively. 
The inner product, $\langle h_1, h_2 \rangle$, is defined as 
\begin{align}\label{eq:inner_prod}
	\langle h_1, h_2 \rangle = 4\Re\int_{f_{\mathrm{min}}}^{f_{\mathrm{max}}}\frac{h_1(f)h_2^{\ast}(f)}{S_n(f)}\,df,
\end{align}
where $\hat{h}=h/\sqrt{\langle h, h \rangle}$ is the normalized GW strain,
$S_n(f)$ is the power spectral density (PSD), and $f_{\mathrm{max}}$ ($f_{\mathrm{min}}$) is
the maximum (minimum) frequency for the integration.
We note here that the mismatch can be viewed as the mean square error (MSE) between the
two waveforms.

@@

The SXS NR waveforms are given as time-series strain.
Since IMRPhenomD is modeled in the frequency domain, we need to Fourier transform the simulation results
in order to compute the mismatch, \eqref{eq:mismatch}.
For this, we taper the time-series using Tukey window~\citep{tukey}\footnote{
	Specifically, we choose $\alpha=2t_{\mathrm{RD}}/T$, where
	$t_{\mathrm{RD}}$ is the duration of ringdown (maximum amplitude to the end of the strain) and $T$ is the duration of the
	entire GW strain. \te{What is $t_{\mathrm{RD}}$? and how is it computed?}
} before using standard FFT routines to compute the Fourier transform.

>>>>

In order to optimize the coefficients, we need to define a loss function that
quantifies the difference between the waveform model and the target NR simulations which we want to match.
Here we adopt a quantity commonly used in GW physics called the \textit{mismatch} function \citep{owen1996search, husa2016frequency}. 
It is defined as
\begin{align} \label{eq:mismatch}
	\mathcal{M}(h_1, h_2)=1-\max_{t_0, \phi_0}\langle \hat{h}_1, \hat{h}_2\rangle,
\end{align}
where $h_{1,2}$ are the two GW waveforms we are comparing, and $t_0$ and $\phi_0$
are a relative time and phase shift respectively. 
The inner product, $\langle h_1, h_2 \rangle$, is defined as 
\begin{align}\label{eq:inner_prod}
	\langle h_1, h_2 \rangle = 4\Re\int_{f_{\mathrm{min}}}^{f_{\mathrm{max}}}\frac{h_1(f)h_2^{\ast}(f)}{S_n(f)}\,df,
\end{align}
where $\hat{h}=h/\sqrt{\langle h, h \rangle}$ is the normalized GW strain,
$S_n(f)$ is the power spectral density (PSD), and $f_{\mathrm{max}}$ ($f_{\mathrm{min}}$) is
the maximum (minimum) frequency for the integration.
We note here that the mismatch can be viewed as the mean square error (MSE) between the
two waveforms.

@@

The SXS NR waveforms are given as time-series strain.
Since IMRPhenomD is modeled in the frequency domain, we need to Fourier transform the simulation results
in order to compute the mismatch, \eqref{eq:mismatch}.
For this, we taper the time-series using Tukey window~\citep{usman2016pycbc}\footnote{
	Specifically, we choose $\alpha=2t_{\mathrm{RD}}/T$, where
	$t_{\mathrm{RD}}$ is the duration of ringdown (maximum amplitude to the end of the strain) and $T$ is the duration of the
	entire GW strain. \te{What is $t_{\mathrm{RD}}$? and how is it computed?}
} before using standard FFT routines to compute the Fourier transform.
